---
title: "MRM Assignment 4"
author: "Isaac Boldery"
date: "10/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library('tidyverse')
library('janitor')
```

## Exercise 1:

# a) The question being asked is whether or not more "nameable" features make a certain category easier to construct and learn.

# b,c)
```{r}
zl_data <- read.csv('https://osf.io/u7xmd/download')
```

# d)
```{r}
glimpse(zl_data)
```

Glimpse shows us that there are 77 variables in the dataframe.

# e)
```{r}
zl_clean <- zl_data %>%
  select('experiment', 'subject', 'Age', 'condition', 'blockNum', 'isRight') %>%
  clean_names()

zl_clean
```
This tibble presents the data in a snakecase and tidy format. 

# f)
```{r}
zl_exp1a <- zl_clean %>%
  filter(experiment == '1A')
zl_exp1a
```

This tibble contains only the 1A experiment cases in a snakecase and tidy format.

## Exercise 2:

# a) 
```{r}
num_of_participants1A <- zl_exp1a %>%
  distinct(subject) %>%
  count()

num_of_participants1A
```

There were 50 participants in the 1A experiment and this confirms what is reported in the paper. 

# b)
```{r}
mean_age_of_participants1A <- zl_exp1a %>%
  summarise(mean(age))

mean_age_of_participants1A
```

The mean age of the participants in the 1A experiment was 32 years. This also matches with what was reported in the paper.

# c)
```{r}
accuracy_across_condition <- zl_exp1a %>%
  group_by(condition) %>%
  summarise(accuracy = sum(is_right)/n())
```

# d)
```{r}
zl_exp1a_new <- zl_exp1a %>%
  group_by(block_num, condition) %>%
  summarise(accuracy = sum(is_right)/n()) %>%
  ungroup()

ggplot(zl_exp1a_new, aes(x=block_num, y=accuracy, color = condition)) +
  geom_line() +
  geom_point() +
  xlab('Block') +
  ylab('Training Accuracy') +
  ylim(0.5,1) +
  geom_hline(aes(yintercept = 0.5))
```

## Exercise 3:

This exercise was completed on github.

## Exercise 4:

# a) 

In the terminal, I used git clone on https://github.com/ChefBoldery/MRM_Assignment_4

# b) I also changed the working directory in the terminal using cd MRM_Assignment_4

## Exercise 5:

# a,b)

Ran both in terminal:

/cloud/project/MRM_Assignment_4$ git config --global user.email "isaac.boldery@gmail.com"

/cloud/project/MRM_Assignment_4$ git config --global user.name "Isaac Boldery"

## Exercise 6:

# a,b,c,d) 

All the code was run in the terminal with no issues. 

## Exercise 7: 

# a) 

readme.md committed with changes

# b) 

After the commit, git status shows that there is nothing ready to commit. The message "working tree clean" is also printed. 

## Exercise 8: 

# a)

Added my favorite picture of a moose :)

# b,c,d)

git status now shows that my branch is ahead of origin by 1 commit which is the picture file. 

## Exercise 9:

# a)

I used git commit and added a message saying "Added a picture of a moose :)."

# b) 

Git status shows that there is nothing to commit and that my working tree is clean. Also, that my branch is ahead of the origin/main by 2 commits which includes the change in the README.md file and the addition of the photo.
